%!TEX TS-program = xelatex
\documentclass[]{friggeri-cv}
\usepackage{soul}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage{mdframed}

\newcommand{\myul}[2][black]{\setulcolor{#1}\ul{#2}\setulcolor{black}}


\begin{document}

\setlist{nolistsep}

\header{Costanza Maria }{Improta}
       {Research Assistant, Master's in Computer Science at ETH Zürich | Master's Thesis at Disney Research}
       

\begin{aside}
  \section{\myul[red]{Contacts}}
    \bigskip
    Weinbergstrasse 97, 8006, Zürich
    +41 78 68 78 797
    \href{mailto:costanza.improta@live.it}{costanza.improta@live.it}
    \href{https://www.linkedin.com/in/cmimp}{linkedin.com/in/cmimp}
    GitHub: \href{https://github.com/cmimprota}{cmimprota}
    ~
  \section{\myul[red]{Programming Competencies}}
    \bigskip
    \textbf{\emph{High Competence:}}
    Python
    C++
    Java
    Tensorflow
    PyTorch
    PyTorch3d
    LaTeX
    
    \bigskip
    \textbf{\emph{Medium Competence:}}
    C
    OpenGL
    HTML5 \& CSS3
    JavaScript \& JQuery
    SQL
    MATLAB
    SoapUI
    Django
    
    \bigskip
    \textbf{\emph{Beginner:}}
    Verilog
    Swift
    Drools
    ~
  \section{\myul[red]{Tools}}
    \bigskip
    Blender
    Affinity
    Unity
    Meshlab
    ~  
  \section{\myul[red]{Certificates}}
    \bigskip
    Google Project Management: Professional Certificate
    ~
  \section{\myul[red]{MOOCs}}
    \bigskip
    \href{http://cs229.stanford.edu}{CS229}
    \href{http://cs231n.stanford.edu/2018/}{CS231n}
    \href{http://cs224d.stanford.edu}{CS224d}
    \href{http://course.fast.ai}{fast.ai}
\end{aside}

\section{\color{red}Education}
\begin{entrylist}
    \entry
    {}
    {\large\emph{\href{https://inf.ethz.ch/studies/master/master-cs.html}{ETH Zürich}}}
    {\textbf{09/2019 - 10/2021}}
    {\large\emph{MSc in Computer Science - Visual Computing track}}
    {Achieved a 6 (100\%) in \emph{Deep Learning for Computer Vision}, \emph{Data Science in Techno-Socio-Economic Systems} and \emph{Shape Modeling and Geometry Processing}}\\
    \begin{itemize}
        \item Strong interest in Data Analysis and Visualization, ML, Computer Vision and Image Processing, NLP and UX/UI.
        \item \emph{PandeML} - built and compared different ML models to correctly predict the COVID-19 pandemic in various countries.
        \item \emph{CSR: Character-level Sequence Representation for Classification of Tweets with Misspellings} - developed a character-level sequence representation  model for sentiment classification of user-generated social media posts.
    \end{itemize}
\medskip
  \entry
    {}
    {\large\emph{\href{http://www.manchester.ac.uk/}{The University of Manchester}}}
    {\textbf{09/2015 - 06/2019}}
    {\large\emph{BSc in Computer Science with Industrial Experience} - First Class Degree}
    {Certificate of Excellence, awarded to top 10\% of graduating students}
    \begin{itemize}
        \item Third Year Project - ``A Dense Captioning Approach to generate a Descriptive \\Paragraph of an Image"
        \item \emph{Eventlite} - developed in a team a MVC web application for event management, using the Spring framework, Google and Twitter APIs.
        \item \emph{\href{https://stendhalgame.org/}{StendhalGame.org}} - as part of a team, tested, debugged, built, developed and deployed a multi-user, multi-threaded, client-server open source game containing 6000+ Java classes and 1800+ test cases using Eclipse, Git, Apache Ant, Jenkins and JUnit.
        \item \emph{ShelfShare} - implemented in a team a platform on which UoM students may securely trade their goods.
    \end{itemize}
\end{entrylist}

\section{\color{red}Work \color{gray} Experience}
\begin{entrylist}
  \entry
    {}
    {\large{Master's Thesis in Industry (Research)}}
    {\textbf{04/2021 - 10/2021}}
    {\large\emph{{Disney Research Studios}, Zürich, Switzerland}}
    \vspace{-4mm}
    \begin{itemize}
        \item Developed a state-of-the-art neural rendering pipeline, to improve rendering quality of coarse image-based 3D reconstructions, achieving a 5.75.
    \end{itemize}
\end{entrylist}
\smallskip
\begin{entrylist}
  \entry
    {}
    {\large{Programming Research Assistant}}
    {\textbf{09/2020 - 11/2021}}
    {\large\emph{{ETH Zürich}, Zürich, Switzerland}}
    \vspace{-4mm}
    \begin{itemize}
        \item Supported researchers in coding experiments, data analysis and empirical research.
    \end{itemize}
\end{entrylist}
\smallskip
\begin{entrylist}
  \entry
    {}
    {\large{Software Engineer}}
    {\textbf{06/2019 - 07/2019}}
    {\large\emph{{The University of Manchester}, Manchester, United Kingdom}}
    \vspace{-4mm}
    \begin{itemize}
        \item Built a data-heavy, web-based application, including restricting access to certain views.
        \item Identified missing features and access limitations.
        \item Designed and developed UI.
    \end{itemize}
\end{entrylist}
\smallskip
\begin{entrylist}
  \entry
    {}
    {\large{Software Engineer}}
    {\textbf{07/2017 - 07/2018}}
    {\large\emph{\href{https://www.isa-software.com}{ISA Software}, Paris, France}}
    ISA Software is an Air Traffic Management Consultancy Company.
    \begin{itemize}[topsep=0pt]
        \item Researched and evaluated ML models to reliably predict air traffic collisions.
        \item Developed and shipped an interactive simulation tool to display and analyse air traffic.
        \item Developed an automated track analysis and anomaly detection tool.
    \end{itemize}
\end{entrylist}
\smallskip
\begin{entrylist}
  \entry
    {}
    {\large{Web Developer, Business Analyst, Italian Interpreter}}
    {\textbf{07/2016 - 08/2016}}
    {\large\emph{\href{http://www.wyng43.com/}{Wyng43}}, Hong Kong, HK}.
    \vspace{-4mm}
    \begin{itemize}
        \item Designed and developed a website for \href{http://www.wyng43.com/}{Wyng43}.
    \end{itemize}
\end{entrylist}
\clearpage
\newpage

\header{Costanza Maria }{Improta}
       {UK's Top 10 Computer Science Undergraduate of 2018 by TARGETjobs and FDM}
       
\begin{aside}
  
  \bigskip
  \section{\myul[red]{Qualifications}}
  \extraspace{Google Summer of Code 2020}
  \extraspace{Google Developer Challenge Scholarship}
  \bigskip
  \textbf{LANGUAGES}\smallskip
  \textbf{Italian:}
  Native speaker\smallskip
  \textbf{English:}
  Bilingual IB Diploma
  IELTS
  CAE\smallskip
  \textbf{French:}
  DELF B1\smallskip
  \textbf{German:}
  A2\smallskip
  \textbf{Chinese:}
  A1\bigskip
  \textbf{COMPUTER SCIENCE}
  UK's Top 10 CS Undergraduate of 2018\smallskip
  IBM UTC Prize
  \bigskip
  \textbf{MATHEMATICS}
  ``Best in Year" \& ``Silver" \\ in \href{https://www.ukmt.org.uk/}{UKTM} (2013)\smallskip
  ``Best in School" \\ in Giochi Matematici 2012
  \bigskip
  \textbf{OTHERS}
  Computer Science, Italian and English \\ ``Best in Year" awards \\ at SGBIS in 2015
  ~
  
  \section{\myul[red]{Hackathons}}
  \bigskip
  Finalist at \\ \href{https://hackzurich.com}{HackZurich 2020}
  ~
  
  \section{\myul[red]{Given talks}}
  \bigskip
  \href{http://www.ibo.org/about-the-ib/the-ib-by-region/ib-africa-europe-middle-east/aem-regional-conference/2014-regional-conference/}{IBAEM Regional Conference 2014}
  ~
  
\end{aside}

\setlist[itemize]{noitemsep, topsep=0pt}

\section{\color{red}Volunteering \color{gray} \& Relevant Activities}
\entry
    {}
    {\href{https://driverless.amzracing.ch}{AMZ Racing - Public Relations Officer (PRO)}}
    {\textbf{09/2020 - present}}
    {\emph{Akademischer Motorsportverein Zürich - ETH Zürich Formula Student Project}}
    \begin{itemize}
        \item Marketing \& PR responsible, focusing on sponsorships,  networking, events and exhibitions.
        \item Managing all social media accounts, and devising an effective social media strategy.
        \item Developing and maintaining both the \href{https://driverless.amzracing.ch/en/home}{AMZ driverless} and \href{https://electric.amzracing.ch/en/home}{AMZ electric} websites.
        \item Previously a core team member in the driverless division, focusing on operations.
        \item Organised the AMZ 2021 roll-out to present our newly built cars for the 2020/2021 season. Mainly focused on marketing \& PR, indoor show and media generation.\\
    \end{itemize}
\entry
    {}
    {\href{http://www.pass.manchester.ac.uk/}{PASS 1 Coordinator}}
    {\textbf{07/2018 - 06/2019}}
    {\emph{The University of Manchester School of Computer Science}}
    \begin{itemize}
        \item Managed PASS sessions for 250+ year one students and their second year leaders.
        \item Led and ran debrief sessions for second year PASS leaders to help them develop and improve their mentoring sessions.
        \item This improved organizational, communication and public speaking skills.\\
    \end{itemize}
\entry
    {}
    {\href{http://www.stemnet.org.uk/ambassadors/}{STEM Ambassador}}
    {\textbf{01/2016 - 06/2019}}
    {\emph{\href{http://www.stemnet.org.uk/}{STEMNET}}}
    \begin{itemize}
        \item Organised activities and talks to inspire young students to pursue a career in a scientific subject and to narrow down the gender gap by engaging girls too.
        \item Worked both in a team and on my own, which gave me the chance to improve my organisational, communication and oratorical skills.\\
    \end{itemize}
   \entry
    {}
    {Student Ambassador, Welcome Hero \& HelpDesk Assistant}
    {\textbf{09/2016 - 06/2019}}
    {\emph{The University of Manchester}}
    \begin{itemize}
        \item Was a reference point for the new students, pointing them in the right direction and making them feel welcome. 
        \item Worked in close contact with members of Academic Staff during Interview Days, talking to prospective students about my current experience, taking them for a tour of the building and answering related questions. 
        \item Through this, I developed leadership, communication and customer service skills.\\
    \end{itemize}
  \entry
    {}
    {\href{http://www.pass.manchester.ac.uk/}{PASS Leader}}
    {\textbf{09/2016 - 06/2017}}
    {\emph{The University of Manchester School of Computer Science}}
    \begin{itemize}
        \item Along with my co-leader, held weekly one-hour meetings with a group of tutees from the year below, supporting their learning process through visual or kinaesthetic activities and giving advice relative to university or life issues. My leadership and communication skills benefited from this.\\
    \end{itemize}
  \entry
    {}
    {\href{http://manchestersciencecity.com/inspire/article/the-robots-are-coming/}{Manchester Robot Orchestra}}
    {\textbf{11/2015 - 2016}}
    {\emph{Manchester European City of Science 2016}}
    \begin{itemize}
        \item Participated in the designing phase - my role was to brainstorm about the various tools and technologies that could be used in order to be time and cost-efficient. This project has also featured contributions from Siemens and The Halle Orchestra.
    \end{itemize}

\clearpage
\end{document}